### 2023-09-23 spanish/sections/languages.tex
LPPL v1.3c
Update languages.tex

\cvskill
{Idiomas} 
{Español (hablante nativo), inglés (fluido), portugués (habilidades de lectura avanzadas),}

\cvskill
{} 
{francés (habilidades de lectura elementales)} \\

\cvskill
{Programación \&} 
{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}

\cvskill
{software} 
{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}} \\

>>>>

\cvskill
{Idiomas} 
{\textcolor{black}{Español (hablante nativo), inglés (fluido), portugués (habilidades de lectura avanzadas),}}

\cvskill
{} 
{\textcolor{black}{italiano (habilidades de lectura elementales), francés (habilidades de lectura elementales)}} \\

\cvskill
{Programación \&} 
{\textcolor{black}{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}

\cvskill
{software} 
{\textcolor{black}{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
